\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/introduction.tex
fix saying of Xiaomi

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.
Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as some non-flagship products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.

>>>>

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.
Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.
